### 2020-12-03 doc/manuscript/Dow_manuscript.Rmd
working on text... slower than hoped!
FYI, @camerondow35 , I'm tyring to make some progress now,

## ("limitation in filling gap, how to interpret/fix")

>>>>

## ("limitation in filling gap, how to interpret/fix")
Although the number of years analyzed here is limited (# years at SCBI, # years at HF), the signal is clear and consistent: for both species groups at both sites, warmer temperatures during virtually any part of the spring led to significantly earlier achievement of growth milestones (*CITE RELEVANT FIGS & TABLES* ).
This indicates that this is not a subtle effect.
However, the effect on L_PGS, r_max, and $\Delta DBH$, if any, is subtle, and a much longer record would be needed to detect such effects. 
Fortunately, we were able to get at annual growth using tree-ring data (Fig. `r tree_rings`).
These confirm that the effect of spring temperatures on annual growth is modest and generally not significant, while revealing a slightly more complex picture.
Although spring temperatures prior to May rarely had a significant influence on
